Collaborative Visual Analysis on the Web with RCloud

### 2015-03-31 introduction.tex
more tweaking
intro and related work cleanup, no more missing references

In some way, we have moved far beyond what Tukey imagined:
computing and networking capabilities today far exceed
what was barely imaginable then. 
We argue, on the other hand, that we \emph{develop} our data analysis
solutions, and context in which they become part of the broader issues
being solved in organizations, has not changed as much: the S language
was developed essentially alongside Unix~\cite{TheSSystem}, after all.
We turn our attention to this opportunity to use computation
to support, not only individuals, but entire teams and their
work within larger organizations. In this paper, we contribute the
design of RCloud, together with an interview study conducted over the
course of its development and deployment at AT\&T Labs, where RCloud has
been in use for about two years.

@@

The high level architecture of the prototype system
is shown in figure~\ref{fig:high-level-architecture}.
We chose R as the foundation for our prototype because it is already
the dominant statistical computing language in our lab.
R also has many useful packages for data analysis and visualization,
and the core system and its packages are open source that can be modified to
support research.

@@

Over the past two \gordon{three?} years, we prototyped RCloud and deployed it to
a community of data scientists, business analysts and other colleagues.  The
platform today has over 300 active accounts; about 20 people use it regularly,
another 30 people use it more than once a week, and another 50 use it more than
once a month.  Most of the
active users are members of AT\&T Labs, but some are data scientists and other
collaborators in other business units.

>>>>

In some way, we have moved far beyond what Tukey imagined:
computing and networking capabilities today far exceed
what was barely imaginable then. 
We argue, on the other hand, that how we \emph{develop} our data analysis
solutions has not changed as much: the S language
was developed essentially alongside Unix~\cite{TheSSystem} and,
although environments such as RStudio include a variety of modern
features, they still follow the basic metaphor of terminal, text
editor, and source files stored in file systems.
We turn our attention to this opportunity to use computation
to support, not only individuals, but entire teams and their
work within larger organizations. In this paper, we contribute the
design of RCloud, together with an interview study conducted over the
course of its development and deployment at AT\&T Labs, where RCloud has
been in use for about two years.

@@

The high level architecture of the prototype system
is shown in figure~\ref{fig:system}.
We chose R as the foundation for our prototype because it is already
the dominant statistical computing language in our lab.
R also has many useful packages for data analysis and visualization,
and the core system and its packages are open source that can be modified to
support research.

@@

Over the past three years, we prototyped RCloud and deployed it to
a community of data scientists, business analysts and other colleagues.  The
platform today has over 300 active accounts; about 20 people use it regularly,
another 30 people use it more than once a week, and another 50 use it more than
once a month.  Most of the
active users are members of AT\&T Labs, but some are data scientists and other
collaborators in other business units.
